---
title: "Weight of Fish"
author: "Alejandra Magdaleno"
date: "November 9, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

Now build our models

# Perch Model

```{r}
# read in the fishdata
fishdata <- read.csv(file="Fish.csv", header=TRUE)
PerchData <- filter(fishdata,Species=="Perch") %>% select(-Species)
```



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = PerchData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
The best two regresor model for Perch is Height and Width.  This is also the best overall model as measured by adjusted R-squared.   
  
    
  
#  Bream Model

```{r}
# read in the fishdata
fishdata <- read.csv(file="Fish.csv", header=TRUE)
BreamData <- filter(fishdata,Species=="Bream") %>% select(-Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = BreamData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two regresor model for Bream is Length2 and Heigth.  This is also the best overall model as measured by adjusted R-squared.
  
#  Smelt Model

```{r}
# read in the fishdata
fishdata <- read.csv(file="Fish.csv", header=TRUE)
SmeltData <- filter(fishdata,Species=="Smelt") %>% select(-Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = SmeltData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two regresor model for Smelt is Length2 and Width.  This is also the best overall model as measured by adjusted R-squared.

# Discussion and Final Conclusion

The best regression model for predicting the weight of Perch is the one using Heigth and Width.  For Bream, the best regression model for predicting the weight is using Length2 and Height.  Finally, the best regression model for predicting the weight of Smelt is Length2 and Width.  All of these are also the best regression models as measured by their individual adjusted R-squared.  

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
